The process of doing research for this thesis has certainly been beneficial for me in several regards. I became familiar with techniques used for HEP analysis.
Several crucial skills were obtained and they are going to be immensely helpful in my future career. These include
\begin{enumerate}
\item Learning to work on Linux OS, which included interacting via \texttt{bash} to connect to CERN servers and run scripts.
\item Learning the basics of the C++ programming language.
\item Learning to effectively manage produced data.
\end{enumerate}

Although the project was concluded on time, I feel that my time could have been spent more productively, especially in the first half of the thesis period. A lot of time then was spent on revising things, and , in hidnsight, that could have taken much less time.
Among personal shortcomings I would like to point out that communication from my side could have been much better. Many issues in the beginning and further on could have been avoided if I articulated my problems and questions earlier. This way I could have achieved more with this thesis. My time management skills need to be improved as well. Procrastination is very punishing on the quality of work and the resulting text. 

Overall, doing this research was very enjoyable. It also was challenging and prompted me to acquire knowledge and skills I will certainly use in the future. 

I would like to thank Dr. Sara Williams for providing me with this opportunity and for being a wonderful thesis supervisor.

